\bf Interactive Visualization of Hierarchically Structured Data

### 2017-03-24 treelapse.tex
Reduce structssi figure size
Update figure legend order (pregnancy)
Also, add weiland fellowship.

\if0\blind
{
  \title{\bf Interactive Visualization of Hierarchically Structured Data}
  \author{Kris Sankaran\thanks{
      This research was supported in part by an NIH training grant (5T32GM096982-03).}\hspace{.2cm}\\
    Department of Statistics, Stanford University\\
    and \\
    Susan Holmes\thanks{
       This research was supported in part by NIH grant R01 AI112401.
      }\hspace{0.2cm}\\
    Department of Statistics, Stanford University}
  \maketitle
} \fi

@@

Our motivating application is to the analysis of microbial time
series, where an evolutionary tree relating microbes is available a
priori. However, we have identified common problem types where, if a
tree is not directly available, it can be constructed from data and
then studied using our techniques. We perform detailed case studies to
describe the alternative use cases, interpretations, and utility of
the proposed visualization methods.

@@

Alternatively, in Figure \ref{fig:pretermcsts}, we avoid working with
CSTs, displaying instead averages among samples associated with either
preterm or term births. The green edges are associated with preterm
births -- we see that they contribute more weight to phyla outside the
Firmicutes. This is consistent with the claim that CST 4, the most
diverse of the CSTs, is associated with preterm births.

@@

{\centering \includegraphics[width=350px]{figure/structssi}

>>>>

\if0\blind
{
  \title{\bf Interactive Visualization of Hierarchically Structured Data}
  \author{Kris Sankaran\thanks{
      This research was supported in part by an NIH training grant (5T32GM096982-03) and a Weiland Fellowship.}\hspace{.2cm}\\
    Department of Statistics, Stanford University\\
    and \\
    Susan Holmes\thanks{
       This research was supported in part by NIH grant R01 AI112401.
      }\hspace{0.2cm}\\
    Department of Statistics, Stanford University}
  \maketitle
} \fi

@@

Our motivating application is to the analysis of bacterial time
series, where an evolutionary tree relating bacteria is available a
priori. However, we have identified common problem types where, if a
tree is not directly available, it can be constructed from data and
then studied using our techniques. We perform detailed case studies to
describe the alternative use cases, interpretations, and utility of
the proposed visualization methods.

@@

Alternatively, in Figure \ref{fig:pretermpreterm}, we avoid working with
CSTs, displaying instead averages among samples associated with either
preterm or term births. The red edges are associated with preterm
births -- we see that they contribute more weight to phyla outside the
Firmicutes. This is consistent with the claim that CST 4, the most
diverse of the CSTs, is associated with preterm births.

@@

{\centering \includegraphics[width=250px]{figure/structssi}
